Hurricane Evacuation Strategies for the State of Mississippi

### 2015-11-16 manuscript.tex
A

\pagestyle{fancy}
\fancyhead{}
\lhead{Chesnais, Pourchet, Vogan}
\chead{Hurricane Evacuation Strategies}
\rhead{\today}
\fancyfoot{}
\rfoot{\thepage}
\lfoot{\includegraphics[height=20pt]{Logo}}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

@@

\section{Model Assumptions}
\label{sec:assumptions}

@@

\section{Individual Contributions}
\label{sec:contributions}
  \begin{thebibliography}{9}
    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
    \bibitem{ms_highways}
      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
  \end{thebibliography}

>>>>

\pagestyle{fancy}
\fancyhead{}
\lhead{Chesnais, Pourchet, Vogan}
\chead{Hurricane Evacuation Strategies}
\rhead{November 16, 2015}
\fancyfoot{}
\rfoot{\thepage}
\renewcommand{\headrulewidth}{0.5pt}
\renewcommand{\footrulewidth}{0.5pt}

@@

\section{Model Assumptions}
\label{sec:assumptions}
  The MSEMA specified that our plan should be enacted on a per-county basis. As you can see in the following figure, these counties are approximately equally sized:
  \begin{figure}[H]
  \centering
  \includegraphics[text=.5\textwidth]{imgs/county_map.png}
  \caption{A map of counties in Mississippi\cite{county_map}}
  \end{figure}

@@

\section{Individual Contributions}
\label{sec:contributions}
  \begin{thebibliography}{9}
    \bibitem{county_map}
      \url{http://www.madeinmississippi.us/wp-content/uploads/2015/02/mississippi-county-map.jpg}
    \bibitem{pmc}
      \url{http://www.ncbi.nlm.nih.gov/pmc/articles/PMC4060166/}
    \bibitem{ms_highways}
      \url{https://www.mississippi.org/assets/docs/library/ms_highways.pdf}
  \end{thebibliography}
